%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{orange} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Guilherme} % Your first name
\familyname{Silva} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Software Engineer}
\address{Manaus - Amazonas}{\href{https://www.linkedin.com/in/guilherme-silva-ab462b39}{https://www.linkedin.com/in/guilherme-silva-ab462b39}}
\mobile{+55 (92) 982276177}
\email{guilherme.mdasilva@gmail.com}
%\photo[70pt][0.4pt]{picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)


%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Summary}

I am a software developer with over 5 years of professional experience. 
I have worked on Web (server and front end side) and mobile applications. 
I have strong knowledge about Java and Android.
I have a solid background to create web and mobile applications.
I have experience in the full life cycle of software development right from requirements gathering,
design, prototype, managing schedule, development, testing and maintenance.

\section{Areas of Expertise}

\cvitem{}{Java programming skill and experience}
\cvitem{}{Mobile applications development for Android}
\cvitem{}{Skilled in the development of cross-platform and embedded applications}
\cvitem{}{Experience with Search Engine libraries such as Lucene and Elastic Search}
\cvitem{}{Experience with Machine Learning techniques}
\cvitem{}{Familiar with Agile development techniques}

\section{Technical skills}

\cvitem{OS}{Linux/Unix, Windows, OSX}
\cvitem{programming}{Java, Android, Python, C, Javascript, Scala, HTML5, CSS3, PHP}
\cvitem{databases}{MySQL, MongoDB}
\cvitem{version control}{GIT, SVN, Perforce}
\cvitem{process}{SCRUM, Jira, Trello, Redmine}

\section{Education}

\cventry{2012 -- 2014}{Masters in Informatics}{Specialized in Database and Information Retrieval. Federal University of Amazonas}{Amazonas}{Brazil}{\textit{Title: Advertising in Social Networks using User Profiles}}
\cventry{2005 -- 2008}{Bachelor in Computer Science}{Federal University of Amazonas}{Amazonas}{Brazil}{\textit{Title: Using Structure Information to Improve Search in Blogs}}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{jan/2017 (current)}{Software Developer}{\textsc{iTriad/Alcatel}}{Manaus - Amazonas}{}{
\begin{itemize}
\item Developing web applications for Alcatel devices using Firefox OS System to embedded. Working with Javascript, HTML5 and CSS3.
\end{itemize}}

\cventry{aug/2013 -- jan/2017}{Software Developer}{\textsc{Samsung SIDIA}}{Manaus}{}{
\begin{itemize}
\item Development of Android applications aimed for Samsung devices. Worked on a project for State Secretary of Finance, an application which issues invoices for clients, using smartphones and tablets. Worked on Car Mode project for several devices, including Galaxys S4 mini, S5, Note 4, S6, Note 5 etc. Car Mode is an application which assists the driver to perform basic tasks while into the car, using voice and touch commands, including Phone, Messaging, Navigation and Music. Worked on latin american models Android System customization team, developing solutions and fixing system related issues, such as kernel panics, drivers, IMEI, configurations, etc. Worked with Java, C, Python and Javascript.
\end{itemize}}

\cventry{dec/2011 -- mar/2013}{Web Developer}{\textsc{Spix Macaw S/A (NewsMonitor and Busk.com)}}{Sao Paulo}{}{
\begin{itemize}
\item Development of a smart news aggregator. This includes several parts such as data collection, indexing, extraction and news search, as long as related segments such as server maintenance, database planning and tuning. Worked with Java, Scala, Python, Javascript, MySQL and Elastic Search.
\end{itemize}}

\cventry{sep/2011 -- dec/2011}{Software Developer}{\textsc{HRT Oil \& Gas}}{Manaus}{}{
\begin{itemize}
\item Development of a software to assist and control the transportation of passengers and cargo from the logistics department. Worked with Django/Python.
\end{itemize}}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{Portuguese}{Native}{}
\cvitemwithcomment{English}{Fluent}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Publications}

\cvitem{}{\textbf{Pick Me Up!}: Location Share App - https://goo.gl/Iw6FJG}


%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage

\recipient{HR Department}{} % Letter recipient
%\date{\today} % Letter date
\opening{Dear Hiring Manager,} % Opening greeting
\closing{Best regards,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

\makelettertitle % Print letter title

%Dear Hiring Manager,
%My name is Raj M. Shah and I am very much interested in an Entry Level C++ Developer's position with %your company.

%My academic program at International Technological University prepared me well for a career in Engineering. I graduated in August 2008 with a Master's degree in Electrical Engineering. As you will note on my enclosed resume, I have supplemented my formal course work with a co-op at Silicon Test Group as a member of Design and Test Engineer. This experience coupled with my academic background makes me an excellent candidate for your Engineering Team.

%I have efficiently worked on C/C++, Digital Systems, Data Processing, CAD/CAE tools. I really enjoy working on each phase of product development cycle because, every time is a new learning experience for me.

%I believe that I am a suitable candidate for this position because, requirement certainly matches with my educational background and skills. On top of that, I have proven my interpersonal skills as an Engineer and that is why people like working me and I hope your team will enjoy too.

%Thank you for your time. I would very much like to meet with you to further discuss my interest in your company. My phone number is (408) 306-6016 and my e-mail address is eerajshah@gmail.com.

%Sincerely,
%Raj M. Shah

I am writing to apply for the Software Developer position at Symbio. I am an IT professional with over 5 years of computer programming experience. In my current role as Software Developer for iTriad (Alcatel R\&D Institute) I work daily to utilize computer programming language in the development of a number of technical projects and assignments.

I am up to date on several computer programming languages and terms. I am incredibly organized and very detail oriented; I avoid making errors at all cost, because I know what even a small mistake can mean to a project. My exemplary programming skills along with my dedication and professionalism make me a well-suited candidate for your Software Developer position. I am also a thorough communicator and work well as part of a team in addition to my ability for self-direction. I would be thrilled to be able to bring my skills and professionalism to your company as a developer.

I am sure you'll find my credentials to be in order and welcome a chance to meet with you to discuss my qualifications. Please do not hesitate to contact me at your convenience. Thank you for your time and I look forward to speaking with you.

Sincerely,

Guilherme Monteiro da Silva

\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}